\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.tex
Updates

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
  pdfauthor={Mushfiqul Anwar Siraji1 \& Rafael Robert Lazar2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

@@

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
\author{Mushfiqul Anwar Siraji\textsuperscript{1} \& Rafael Robert Lazar\textsuperscript{2}}
\date{}

@@

The authors made the following contributions. Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Writing - Original Draft Preparation.

Correspondence concerning this article should be addressed to Mushfiqul Anwar Siraji, Monash University, Malaysia. E-mail: \href{mailto:mushfiqul.anwarsiraji@monash.edu}{\nolinkurl{mushfiqul.anwarsiraji@monash.edu}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

@@

@@

@@

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.

@@

@@

\begin{verbatim}
## Call: mardia(x = LB.cfa, na.rm = T, plot = F)
## 
## Mardia tests of multivariate skew and kurtosis
## Use describe(x) the to get univariate tests
## n.obs = 199   num.vars =  48 
## b1p =  761.72   skew =  25263.82  with probability  <=  8.8e-152
##  small sample skew =  25660.39  with probability <=  1.2e-171
## b2p =  2540.5   kurtosis =  14.3  with probability <=  0
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 64 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        79
##                                                       
##   Number of observations                           199
##   Number of missing patterns                         1
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                406.275     387.999
##   Degrees of freedom                                220         220
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   1.047
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1700.445    1368.235
##   Degrees of freedom                               253         253
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.243
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.871       0.849
##   Tucker-Lewis Index (TLI)                       0.852       0.827
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.873
##   Robust Tucker-Lewis Index (TLI)                            0.854
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -6371.304   -6371.304
##   Scaling correction factor                                  1.877
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -6168.166   -6168.166
##   Scaling correction factor                                  1.266
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               12900.607   12900.607
##   Bayesian (BIC)                             13160.778   13160.778
##   Sample-size adjusted Bayesian (BIC)        12910.502   12910.502
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.065       0.062
##   90 Percent confidence interval - lower         0.055       0.052
##   90 Percent confidence interval - upper         0.075       0.072
##   P-value RMSEA <= 0.05                          0.007       0.026
##                                                                   
##   Robust RMSEA                                               0.063
##   90 Percent confidence interval - lower                     0.053
##   90 Percent confidence interval - upper                     0.074
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.075       0.075
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 =~                                                                 
##     item31            1.000                               0.397    0.873
##     item33            0.823    0.123    6.685    0.000    0.327    0.724
##     item1             0.990    0.158    6.246    0.000    0.393    0.644
##     item37            0.901    0.284    3.176    0.001    0.358    0.507
##     item24            0.437    0.265    1.647    0.100    0.173    0.175
##   F2 =~                                                                 
##     item10            1.000                               0.859    0.783
##     item47            0.856    0.111    7.729    0.000    0.736    0.808
##     item36            0.945    0.137    6.876    0.000    0.812    0.701
##     item44           -0.714    0.139   -5.131    0.000   -0.613   -0.490
##     item35            0.739    0.139    5.300    0.000    0.635    0.508
##     item13            0.472    0.113    4.163    0.000    0.406    0.373
##   F3 =~                                                                 
##     item43            1.000                               1.291    0.951
##     item26            0.918    0.056   16.313    0.000    1.186    0.843
##     item32            0.895    0.064   13.928    0.000    1.155    0.872
##   F4 =~                                                                 
##     item14            1.000                               0.493    0.263
##     item7             0.640    0.267    2.392    0.017    0.316    0.171
##     item11            1.850    0.684    2.706    0.007    0.912    0.708
##     item42            0.788    0.314    2.513    0.012    0.389    0.225
##     item12            1.953    0.779    2.509    0.012    0.963    0.845
##     item16            1.017    0.410    2.479    0.013    0.501    0.343
##   F5 =~                                                                 
##     item19            1.000                               0.875    0.683
##     item34            1.312    0.174    7.555    0.000    1.148    0.831
##     item2             0.974    0.143    6.827    0.000    0.852    0.606
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 ~~                                                                 
##     F2                0.038    0.033    1.169    0.243    0.112    0.112
##     F3               -0.019    0.051   -0.372    0.710   -0.037   -0.037
##     F4                0.013    0.024    0.532    0.595    0.064    0.064
##     F5                0.027    0.034    0.795    0.427    0.078    0.078
##   F2 ~~                                                                 
##     F3               -0.076    0.076   -0.998    0.318   -0.069   -0.069
##     F4                0.077    0.054    1.443    0.149    0.182    0.182
##     F5               -0.259    0.088   -2.929    0.003   -0.344   -0.344
##   F3 ~~                                                                 
##     F4                0.032    0.065    0.501    0.616    0.051    0.051
##     F5               -0.035    0.103   -0.339    0.735   -0.031   -0.031
##   F4 ~~                                                                 
##     F5               -0.015    0.044   -0.350    0.726   -0.036   -0.036
## 
## Intercepts:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
##    .item24            1.131    0.070   16.129    0.000    1.131    1.143
##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
##    .item7             3.688    0.131   28.175    0.000    3.688    1.997
##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
##     F1                0.000                               0.000    0.000
##     F2                0.000                               0.000    0.000
##     F3                0.000                               0.000    0.000
##     F4                0.000                               0.000    0.000
##     F5                0.000                               0.000    0.000
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.049    0.032    1.533    0.125    0.049    0.237
##    .item33            0.097    0.058    1.678    0.093    0.097    0.476
##    .item1             0.217    0.058    3.718    0.000    0.217    0.585
##    .item37            0.370    0.125    2.952    0.003    0.370    0.743
##    .item24            0.948    0.200    4.729    0.000    0.948    0.969
##    .item10            0.465    0.130    3.582    0.000    0.465    0.386
##    .item47            0.287    0.054    5.359    0.000    0.287    0.347
##    .item36            0.683    0.094    7.283    0.000    0.683    0.509
##    .item44            1.187    0.139    8.551    0.000    1.187    0.760
##    .item35            1.160    0.156    7.447    0.000    1.160    0.742
##    .item13            1.019    0.112    9.133    0.000    1.019    0.861
##    .item43            0.175    0.101    1.726    0.084    0.175    0.095
##    .item26            0.573    0.164    3.500    0.000    0.573    0.289
##    .item32            0.422    0.114    3.694    0.000    0.422    0.240
##    .item14            3.264    0.236   13.831    0.000    3.264    0.931
##    .item7             3.311    0.274   12.104    0.000    3.311    0.971
##    .item11            0.831    0.172    4.816    0.000    0.831    0.499
##    .item42            2.835    0.171   16.555    0.000    2.835    0.949
##    .item12            0.373    0.155    2.413    0.016    0.373    0.287
##    .item16            1.885    0.199    9.453    0.000    1.885    0.882
##    .item19            0.877    0.130    6.769    0.000    0.877    0.534
##    .item34            0.592    0.179    3.319    0.001    0.592    0.310
##    .item2             1.252    0.144    8.687    0.000    1.252    0.633
##     F1                0.158    0.033    4.750    0.000    1.000    1.000
##     F2                0.738    0.147    5.035    0.000    1.000    1.000
##     F3                1.667    0.246    6.764    0.000    1.000    1.000
##     F4                0.243    0.170    1.431    0.152    1.000    1.000
##     F5                0.766    0.164    4.669    0.000    1.000    1.000
## 
## R-Square:
##                    Estimate
##     item31            0.763
##     item33            0.524
##     item1             0.415
##     item37            0.257
##     item24            0.031
##     item10            0.614
##     item47            0.653
##     item36            0.491
##     item44            0.240
##     item35            0.258
##     item13            0.139
##     item43            0.905
##     item26            0.711
##     item32            0.760
##     item14            0.069
##     item7             0.029
##     item11            0.501
##     item42            0.051
##     item12            0.713
##     item16            0.118
##     item19            0.466
##     item34            0.690
##     item2             0.367
\end{verbatim}

\begin{verbatim}
##          gfi         agfi          nfi          rfi   cfi.robust   tli.robust 
##        0.974        0.965        0.761        0.725        0.873        0.854 
## rmsea.robust         srmr          aic 
##        0.063        0.075    12900.607
\end{verbatim}

\begin{verbatim}
##               F1        F2        F3        F4        F5
## alpha  0.6310368 0.4818562 0.9175522 0.5837683 0.7413266
## omega  0.6175478 0.6258140 0.9185279 0.5055608 0.7523535
## omega2 0.6175478 0.6258140 0.9185279 0.5055608 0.7523535
## omega3 0.5953438 0.6255108 0.9183889 0.4373745 0.7559532
## avevar 0.2554061 0.3750499 0.7902138 0.1670288 0.5080283
\end{verbatim}

Based on CFI, TLI, RMSEA and SRMR value the fitted five factor model is not acceptable.
As a result a close inspection on items with low factor-loadings and low R-square value was conducted. two items were found to be problematic \textbf{item7, item 24} with vary low R-square
value thus discarded from the model.

\begin{verbatim}
## lavaan 0.6-9 ended normally after 67 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        73
##                                                       
##   Number of observations                           199
##   Number of missing patterns                         1
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                273.193     263.376
##   Degrees of freedom                                179         179
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   1.037
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1557.809    1230.314
##   Degrees of freedom                               210         210
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.266
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.930       0.917
##   Tucker-Lewis Index (TLI)                       0.918       0.903
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.932
##   Robust Tucker-Lewis Index (TLI)                            0.921
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -5691.495   -5691.495
##   Scaling correction factor                                  1.890
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -5554.899   -5554.899
##   Scaling correction factor                                  1.284
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               11528.990   11528.990

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, Manuel Spitschan3, \& Manuel Spitschan3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

@@

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, Manuel Spitschan\textsuperscript{3}, \& Manuel Spitschan\textsuperscript{3}}
\date{}

@@

The authors made the following contributions. Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.

Correspondence concerning this article should be addressed to Manuel Spitschan, . E-mail:

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia\\\textsuperscript{2} University of Basel}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\begin{figure}

{\centering \includegraphics[width=4.17in,height=0.5\textheight]{Flowchart1}

\caption{ABC}\label{fig:unnamed-chunk-1}
\end{figure}

@@

Our study had four objectives. First, to develop an instrument to assess individual's light exposure behavior . Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. Third to gather structural validity evidence for the latent structure obtained in EFA (Furr, 2014). Lastly, we gathered item information using Item response theory (IRT)(Baker, 2017)

\hypertarget{data-collection}{%
\subsubsection{Data Collection}\label{data-collection}}

Timeline of data collection, ethical approval, mode of data collection, how consent was recorded.

\hypertarget{item-generation-and-content-validity-expert-panel-review}{%
\subsubsection{Item generation and Content Validity: Expert Panel Review}\label{item-generation-and-content-validity-expert-panel-review}}

How we developed the 48 items?

\hypertarget{analytic-strategies}{%
\subsection{Analytic Strategies}\label{analytic-strategies}}

We used R (version 4.1.0), including several R-packages for our analyses. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (pa) a factor extraction method with varimax rotation. PA is apparently robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by weighted least squares (WLS) extraction method as well. We used a combination factor indentification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to identify the simple structure we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018; Child, 2006; Mulaik, 2009; Watkins, 2020)

@@

Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) . The overall KMO vale for 23 items was 0.63 which was above the cutoff value of .50 indicating a mediocre sample (Hutcheson, 1999).

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tabDes}Descriptive Statistics}

\begin{tabular}{llllllll}
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{p} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25 & .00 & .16\\
Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84 & .00 & .14\\
Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79 & .00 & .19\\
Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83 & .00 & .19\\
Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66 & .00 & .38\\
Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87 & .00 & .33\\
Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65 & .00 & .23\\
Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86 & .00 & .00\\
Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69 & .00 & .33\\
Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91 & .00 & .28\\
Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89 & .00 & .35\\
Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83 & .00 & .32\\
Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91 & .00 & .10\\
Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74 & .00 & .32\\
Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60 & .00 & .15\\
Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85 & .00 & .39\\
Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82 & .00 & .05\\
Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86 & .00 & .11\\
Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82 & .00 & .17\\
Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70 & .00 & .13\\
Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41 & .00 & .01\\
Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86 & .00 & .19\\
Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43 & .00 & .21\\
Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43 & .00 & .28\\
Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89 & .00 & .11\\
Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46 & .00 & .36\\
Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67 & .00 & .22\\
Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81 & .00 & .25\\
Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91 & .00 & .14\\
Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76 & .00 & .30\\
Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13 & .00 & .18\\
Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49 & .00 & .31\\
Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10 & .00 & .16\\
Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87 & .00 & .16\\
Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85 & .00 & .19\\
Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87 & .00 & .25\\
Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25 & .00 & .16\\
Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84 & .00 & .18\\
Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71 & .00 & .18\\
Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88 & .00 & .21\\
Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76 & .00 & .43\\
Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83 & .00 & .44\\
Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50 & .00 & .32\\
Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91 & .00 & -.10\\
Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85 & .00 & .20\\
Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80 & .00 & .26\\
Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86 & .00 & .26\\
Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48 & .00 & .24\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}
\includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1} \caption{Iter-correlation of the items}\label{fig:figCor}
\end{figure}

Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. The Shapiro-Wilk test of normality (Shapiro \& Wilk, 1965) indicated all the items violated normality assumptions. Multivariate normality assumptions were investigated by Marida's test (Mardia, 1970). Multivariate skew = 583.80 (p \textless0.001) and multivariate kurtosis = 2,749.15 (p \textless0.001) indicated multivariate normality assumptions violation. Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (Desjardins \& Bulut, 2018). Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA. However only 4.96\% of the inter-item correlation coefficients were greater than .30 in the obtained matrix. The inter item correlation ranged between .44 to .91. The corrected item-total correlations ranged between .10 to .44.

Scree plot ( Fig@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis (Horn, 1965), like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution Parallel analysis is also more immune to the normality assumptions violation(\textbf{RN1263?}).

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/fac.id-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}(\#fig:fac.id)
\end{figure}

@@
